---
title: "US Breweries Overview"
author: "Niki Hashemi"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: 
  html_document:
    number_sections: true
    toc: yes
    toc_float: yes
    code_folding: hide
    theme: yeti
---

```{r setup, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE
)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse,
  janitor,
  pander,
  usmap,
  knitr
)
```

# Introduction

The purpose of this markdown is to provide an in-depth overview of the US Breweries dataset from [Kaggle](https://www.kaggle.com/brkurzawa/us-breweries). 

Details about how the dataset was acquired and an overview of the datapoints are outlined by Brett Kurzawa in Kaggle. 

```{r load_dataset}
# Load Data
data <- readr::read_csv(
  file = "data/breweries_us.csv"
) %>%
  janitor::clean_names()

# Clean Data
data_lite <- data %>%
  dplyr::select(
    brewery_name,
    state
  ) %>%
  dplyr::distinct() %>%
  dplyr::group_by(state) %>%
  dplyr::mutate(count = dplyr::n()) %>%
  dplyr::ungroup() %>%
  dplyr::select(
    state,
    count
  ) %>%
  dplyr::mutate(state = stringr::str_replace_all(state, "-", " ")) %>%
  dplyr::distinct() %>%
  dplyr::arrange(state)
```

# Overview {.tabset}

## Map

The map shows the number of unique breweries per state.

```{r}
usmap::plot_usmap(data = data_lite, values = "count") + 
  ggplot2::scale_fill_continuous(
    low = "white",
    high = "purple",
    name = "Number of Breweries per State",
    label = scales::comma
  ) + 
  ggplot2::theme(legend.position = "right")
```

## Top 10 States

The table shows the 10 states with the most number of unique breweries.

```{r}
data_lite %>%
  dplyr::arrange(desc(count)) %>%
  dplyr::top_n(10) %>%
  dplyr::rename(
    "State" = state,
    "Number of Breweries" = count
  ) %>%
  pander::pander()
```
## Bottom 10 states

The table shows the 10 states with the least number of unique breweries

```{r}
data_lite %>%
  dplyr::arrange(count) %>%
  dplyr::top_n(-10) %>%
  dplyr::rename(
    "State" = state,
    "Number of Breweries" = count
  ) %>%
  pander::pander()
```
